Physcraper: a python package for continual update of evolutionary estimates using the Open Tree of Life

### 2020-07-10 2-body.Rmd
fix refs

Yet, publicly available estimates of phylogenetic relationships still only about 100 000 taxa [@piel2009treebase; @hinchliff2015synthesis; @opentreeoflife_2019_synth].
These data comprise less than one third of the taxonomic diversity for which sequence data was available a decade ago!

@@

While the focus on single locus and gene sequence alignments could appear backwards-looking, in the age of genomics, single locus data has a lot to offer phylogenetics.
One major challenge of inferring phylogenies from genome scale data is inference of homology, and acquiring homologous data across divergent species.
Different research questions call for on different approaches to genomic sequencing, from whole genomes, to transcriptomes, to RadSeq and UCE's.
This variety of approaches results in non-overlapping data sets across taxa.
Even when the same sequencing approach is applied, such as RadSeq phylogenetic distance can cause allelic dropout at deeper divergences [@eaton2016]
In contrast, single locus sequencing generates homologous data across large phylogenetic scales.

@@

```{bash echo= FALSE, include=FALSE, message= FALSE, results='hide'}
wget "https://raw.githubusercontent.com/McTavishLab/physcraperex/master/data-raw/malvaceae-images/cotree-plot2-1.png"
mv cotree-plot2-1.png docs/figs/cotree-plot2-1.png
```
```{r fig-2, echo=FALSE, fig.cap="Comparison of original tree and tree updated with Physcraper, family Malvaceae.", out.width = '85%', fig.retina= 2, fig.align = "center"}
knitr::include_graphics("docs/figs/cotree-plot2-1.png")
```
\newpage

>>>>

Yet, publicly available estimates of phylogenetic relationships still cover only about 100 000 taxa [@piel2009treebase; @hinchliff2015synthesis; @opentreeoflife2019synth].
These data comprise less than one third of the taxonomic diversity for which sequence data was available a decade ago!

@@

While the focus on single locus and gene sequence alignments could appear backwards-looking, in the age of genomics, single locus data has a lot to offer phylogenetics.
One major challenge of inferring phylogenies from genome scale data is inference of homology, and acquiring homologous data across divergent species.
Different research questions call for on different approaches to genomic sequencing, from whole genomes, to transcriptomes, to RadSeq and UCE's.
This variety of approaches results in non-overlapping data sets across taxa.
Even when the same sequencing approach is applied, such as RadSeq phylogenetic distance can cause allelic dropout at deeper divergences [@eaton2016misconceptions]
In contrast, single locus sequencing generates homologous data across large phylogenetic scales.

@@

<!-- ```{bash echo= FALSE, include=FALSE, message= FALSE, results='hide'}
wget "https://raw.githubusercontent.com/McTavishLab/physcraperex/master/data-raw/malvaceae-images/cotree-plot2-1.png"
mv cotree-plot2-1.png docs/figs/cotree-plot2-1.png
``` -->
```{r fig-2, echo=FALSE, fig.cap="Comparison of original tree and tree updated with Physcraper, family Malvaceae.", out.width = '85%', fig.retina= 2, fig.align = "center"}
knitr::include_graphics("docs/figs/cotree-plot2-1.png")
```
\newpage

### 2020-07-10 docs/submission-mee-2020-07-10.tex
fix refs

\textbf{Word count}: 3769

@@

Yet, publicly available estimates of phylogenetic relationships still only about 100 000 taxa ({\textbf{???}}; Piel \emph{et al.} \protect\hyperlink{ref-piel2009treebase}{2009}; Hinchliff \emph{et al.} \protect\hyperlink{ref-hinchliff2015synthesis}{2015}).
These data comprise less than one third of the taxonomic diversity for which sequence data was available a decade ago!

@@

While the focus on single locus and gene sequence alignments could appear backwards-looking, in the age of genomics, single locus data has a lot to offer phylogenetics.
One major challenge of inferring phylogenies from genome scale data is inference of homology, and acquiring homologous data across divergent species.
Different research questions call for on different approaches to genomic sequencing, from whole genomes, to transcriptomes, to RadSeq and UCE's.
This variety of approaches results in non-overlapping data sets across taxa.
Even when the same sequencing approach is applied, such as RadSeq phylogenetic distance can cause allelic dropout at deeper divergences ({\textbf{???}})
In contrast, single locus sequencing generates homologous data across large phylogenetic scales.

@@

@@

>>>>

\textbf{Word count}: 3768

@@

Yet, publicly available estimates of phylogenetic relationships still cover only about 100 000 taxa (Piel \emph{et al.} \protect\hyperlink{ref-piel2009treebase}{2009}; Hinchliff \emph{et al.} \protect\hyperlink{ref-hinchliff2015synthesis}{2015}; OpenTreeOfLife \emph{et al.} \protect\hyperlink{ref-opentreeoflife2019synth}{2019}).
These data comprise less than one third of the taxonomic diversity for which sequence data was available a decade ago!

@@

While the focus on single locus and gene sequence alignments could appear backwards-looking, in the age of genomics, single locus data has a lot to offer phylogenetics.
One major challenge of inferring phylogenies from genome scale data is inference of homology, and acquiring homologous data across divergent species.
Different research questions call for on different approaches to genomic sequencing, from whole genomes, to transcriptomes, to RadSeq and UCE's.
This variety of approaches results in non-overlapping data sets across taxa.
Even when the same sequencing approach is applied, such as RadSeq phylogenetic distance can cause allelic dropout at deeper divergences (Eaton \emph{et al.} \protect\hyperlink{ref-eaton2016misconceptions}{2016})
In contrast, single locus sequencing generates homologous data across large phylogenetic scales.

@@

\leavevmode\hypertarget{ref-eaton2016misconceptions}{}%
Eaton, D.A.R., Spriggs, E.L., Park, B. \& Donoghue, M.J. (2016). Misconceptions on Missing Data in RAD-seq Phylogenetics with a Deep-scale Example from Flowering Plants. \emph{Systematic Biology}, \textbf{66}, 399--412. Retrieved from \url{https://doi.org/10.1093/sysbio/syw092}

@@

\leavevmode\hypertarget{ref-opentreeoflife2019synth}{}%
OpenTreeOfLife, Redelings, B., Reyes, L.L.S., Cranston, K.A., Allman, J., Holder, M.T. \& McTavish, E.J. (2019). Open tree of life synthetic tree. Retrieved from \url{https://doi.org/10.5281/zenodo.3937742}
